Supplementary Information

### 2020-11-18 doc/manuscript/MEE_manuscript_SI.Rmd
knit in new traditional comparison figures

# MOVE FIGURE FILES (doing this because I got an error when using the absolute path to call figures)
#traditional comparison
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/formal_comparison/figures/", "^climwin_vs_dcc_.+[.]png$", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/traditional_comparison/")

# climwin plots
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined/")

#composite plots
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/composite_plots/")

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_SCBI_LITU_pre.png){ width=70% }

@@

![](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_SCBI_LITU_pet.png){ width=70% }

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_Zofin_ABAL_wet.png){ width=70% }

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_Zofin_ABAL_tmx.png){ width=70% }

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_CedarBreaks_PSME_pre.png){ width=70% }

@@

![](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_CedarBreaks_PSME_tmx.png){ width=70% }

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_ScottyCreek_PIMA_pre.png){ width=70% }

@@

![](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_ScottyCreek_PIMA_tmx.png){ width=70% }

>>>>

# MOVE FIGURE FILES (doing this because I got an error when using the absolute path to call figures)
#traditional comparison
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/traditional_comparison/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/formal_comparison/figures/", "^climwin_vs_dcc_.+[.]png$", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/traditional_comparison/")

# climwin plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined/")

#composite plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/composite_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/composite_plots/")

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_SCBI_LITU_pre.png){ width=95% }

@@

![](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_SCBI_LITU_pet.png){ width=95%}

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_Zofin_ABAL_wet.png){ width=95% }

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_Zofin_ABAL_tmx.png){ width=95% }

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_CedarBreaks_PSME_pre.png){ width=95% }

@@

![](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_CedarBreaks_PSME_tmx.png){ width=95% }

@@

![ ](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_ScottyCreek_PIMA_pre.png){ width=95% }

@@

![](tables_figures/SI_figures/traditional_comparison/climwin_vs_dcc_ScottyCreek_PIMA_tmx.png){ width=95% }
